---
title: "Midterm"
author: "Cody Evans"
output:
  pdf_document: default
  html_notebook: default
---

Importing data

```{r}
suppressMessages(library("tidyverse"))
suppressMessages(register <- read_csv("register.csv"))
suppressMessages(sales <- read_csv("sales.csv"))
#N <- nrow(register)
```

## Original column names for the two data sets Register and Sales\n\nRegister\n

```{r}
colnames(register)
```

## \nSales\n

```{r}
colnames(sales)
```

Changing column names for better understanding

``{r}
colnames(register)[colnames(register) == "is the customer a student/faculty/staff (0) or unaffiliated (1)"] <- "unaffiliated"
colnames(register)[colnames(register) == "customer id"] <- "cid"
colnames(register)[colnames(register) == "preferred customer discount"] <- "discount"
colnames(register)[colnames(register) == "contact preference"] <- "contact"

cat("Improved column names for the register data\n")
colnames(register)

colnames(sales)[colnames(sales) == "category of inventory goods"] <- "goods"

cat("Improved column names for the sales data\n")
colnames(sales)
```

## Making some Tibbles

``{r}
people <- tibble(generator = surv$generator, name = surv$name, sex = surv$sex, major = surv$major, grade_level = surv$grade_level, year_born = surv$year_born, instrument = surv$instrument, time = surv$time_sub)

song_list <- tibble(song_artist = surv$song_artist, song = surv$song, link = surv$link, name = surv$name)

tempPref <- pref[2:45]

temp <- gather(tempPref, key = "song_name", value = "rating", -name)

ratings <- tibble(persName = temp$name, songName = temp$song_name, rating = temp$rating)

people$time <- as.POSIXlt(parse_datetime(people$time, format = "%D %H:%M"))

for(n in 1:N) {
  if(identical(x = people$generator[n], y ="Fake rapper name generator")) {   
    people$generator[n] <- "rapper"
  } else {
    people$generator[n] <- "band"
  }
}

## install.packages("pracma")

suppressMessages(library("pracma"))
for(n in 1:N) {
  for(z in 1:N) {
    if(strcmpi(people$major[n], people$major[z])) {
      people$major[z] = people$major[n]
    }
  }
}
detach("package:pracma", unload=TRUE)

people$major <- as.factor(people$major)

levels(people$major)
```